Something about Continuous Deductive Reasoning over Streamed RDF Data, maybe claim Soundness or some other Theoretical Quality

### 2015-06-30 content/contribution/continuous-datalog.tex
separated the discussion of continuous time from the main definition of an 'instant'

\begin{definition}[Instant]\label{def:continuous datalog: instant}
An instant is a discrete point in time.  The continuous distance in
time between these discrete points may be theoretically infinitesimal,
but will in practise have a lower bound set by hardware limitations,
or will be defined as part of some specific implementation.  In these
cases, anything that occurs between discrete instants is considered to
have occurred at the next instant.
\end{definition}

>>>>

\begin{definition}[Instant]\label{def:continuous datalog: instant}
An instant is a discrete point in time, such that an instant ${i \in \mathbb{N}}$.

It should be noted that time is a continuous concept, with infinitely many divisions possible between any two discrete instants.
However, the resolution with which such divisions can be recognised will, in practise, have a lower bound set by hardware limitations, or may be defined as part of some specific implementation.
In these cases, anything that occurs between discrete instants is considered to have occurred at the next recognised instant.
\end{definition}
